---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  fig.retina = 2
)
```

# djprtheme

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/djpr-data/djprtheme/workflows/R-CMD-check/badge.svg)](https://github.com/djpr-data/djprtheme/actions) [![Codecov test coverage](https://codecov.io/gh/djpr-data/djprtheme/branch/main/graph/badge.svg)](https://codecov.io/gh/djpr-data/djprtheme?branch=main)
[![Lifecycle: superseded](https://img.shields.io/badge/lifecycle-superseded-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html#superseded)
<!-- badges: end -->

**This package is under active development**

The goal of `djprtheme` is to enable users to easily create ggplot2 charts that look good and are consistent with the style guide of the Victorian Department of Jobs, Precincts and Regions.

## Installation

You can install `djprtheme` from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("djsir-data/djprtheme")
```

## The DJPR palette

```{r colours, echo=FALSE, include=FALSE}
devtools::load_all()
library(ggplot2)

col_names <- c("djpr_cobalt",
          "djpr_bondi_blue",
          "djpr_lima",
          "djpr_electric_lime",
          "djr_royal_blue",
          "djpr_green",
          "djpr_persimmon",
          "djpr_dark_tangerine",
          "djpr_black_rock",
          "djpr_cool_grey_11",
          "djpr_cool_grey_1")

cols <- c(djpr_cobalt,
          djpr_bondi_blue,
          djpr_lima,
          djpr_electric_lime,
          djpr_royal_blue,
          djpr_green,
          djpr_persimmon,
          djpr_dark_tangerine,
          djpr_black_rock,
          djpr_cool_grey_11,
          djpr_cool_grey_1)

df <- data.frame(col = cols,
                 name = col_names)

ggplot(df,
                aes(x = factor(name, 
                               levels = rev(name)),
                    y = 1,
                    fill = name)) +
  geom_tile() +
  geom_text(aes(label = col),
            col = "white") +
  coord_flip() +
  scale_fill_manual(values = cols) +
  theme_void() +
  theme(axis.text.y = element_text(hjust = 1),
        legend.position = "none")

```

You can style your plots with the DJPR palette using the `djpr_colour_manual()` and `djpr_fill_manual()` functions. You should specify the number of colours in your plot. These are the colours that will be used in your plot:

```{r palette-pyramid, echo=FALSE, warning=FALSE}
make_col_tibble <- function(n) {
  dplyr::tibble(col = suppressWarnings(djpr_pal(n)),
         order = c(1:n),
         n = n)
}

djpr_colours <- lapply(c(1:10), make_col_tibble) %>%
  dplyr::bind_rows()

djpr_colours$col <- factor(djpr_colours$col)

djpr_colours <- djpr_colours %>%
  dplyr::mutate(n_desc = dplyr::if_else(n == 1, "n = 1", paste0("  ", n)))

col_plot <- djpr_colours %>%
  ggplot(aes(x = reorder(n_desc, -n), 
             y = order, 
             fill = col)) +
  geom_tile(col = "white", size = 1) +
  scale_fill_manual(values = levels(djpr_colours$col)) +
  coord_flip(expand = FALSE, ylim = c(0, 13)) +
  theme_djpr() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  labs(title = "These are the colours of the DJPR palette")

col_plot
```

The hex codes for those colours are:

```{r palette-hex-codes, echo = FALSE, warning = FALSE}
hexes <- suppressWarnings(djpr_pal(10))

hex_df <- data.frame(hex = hexes,
       row = -seq_along(hexes))

ggplot(hex_df, aes(y = row, fill = hex, label = hex, x = 1)) +
  geom_tile() +
  geom_text(aes(label = hex), colour = "white") +
  scale_fill_identity()  +
  theme_void()

```
